---
title: "Easy Test 1 for xgboost"
author: "Aditya Samantaray"
date: "20/3/2019"
output:
  html_document:
    df_print: paged
  pdf_document: default
---
# Easy Test 1 for xgboost

We'll try to fit a model using xgboost function for the "Insurance" dataset. We'll try to predict the ratio of insurance claims per holder using poisson regression.  

## Loading the packages
```{r loading}
library("xgboost")
library(directlabels)
library(data.table)
library("Matrix")
library(caret)
data("Insurance", package = "MASS")
Insurance$freq<-with(Insurance, (Claims/Holders) ) #Creating a label frequency
head(Insurance)
train.X <- Insurance[-c(4,5)]
train.X <- sparse.model.matrix(freq~., Insurance)
train.Y <- Insurance$freq
```
  
## Plotting the frequency data(Number of claims/Number of holders for each datapoint)
```{r plot}
ggplot(Insurance, aes(x = freq))+
  geom_density(alpha = 0.2, fill="#FF7777")+
  ggtitle("Frequency Distribution")
```
We see that the plot produced resembles a poisson distribution. Hence we can perform poisson regression  

## Performing 5 fold CV
```{r cv}
param <- list(  objective   = "count:poisson", #Setting the objective parameter to count:poisson
                eta         = 1,
                max.depth   = 3,
                nthread     = 2
)
fit <- xgb.cv(params = param, data = train.X, label = train.Y, nfold = 5, nrounds = 5, showsd = F, prediction = T)
pred <- round(fit$pred)
error <- (pred - train.Y)^2
#Baseline error calculation
errbaseline <- (sum(abs(replace(train.Y, c(1:64), mean(train.Y)) - train.Y)))/length(train.Y)
```
  
## Plotting the results
```{r final}
df <- data.frame("ID" = factor(rep(1:2, each = 64)), "TestError" = c(error, rep(errbaseline, each = 64))*100)
df$ID <- ifelse(df$ID == 1, "Model", "Baseline") #ID 1 for prediction, ID 2  for baseline

#Plotting
p <- ggplot(df, aes(x = c(rep(1:64, 2)), y = TestError, colour = ID))+
  geom_line()+
  ggtitle('Model Error over Baseline') +
  xlab('Data Points') +
  ylab('Test Error (in %)')
direct.label(p, "angled.boxes")
```
